2-factor-Hull-White\_model\_calibration

### 2020-05-12 week7/Report.tex
Conclusion

\section{Conclusion}

>>>>

\section{Conclusion}
In this paper, we simulated correlated firm and share price paths. From this, we priced an up-and-out call option at 8.299 with a default-free risk profile, and at 8.281 for the CVA-adjusted price. Considering that the same parameters are used as the first submission, where the Black-Scholes-Merton model was used to arrive at a price of 5.697, we observe that both the default risk, the variable interest rate and local volatility have all added a premium to the option price. These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2\% of the difference. These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.
